Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-06-27 MUSES_vs_BYOD_solutions.tex
Including more information about how te different kinds of data are used in the EC methods

\item A \textit{GP rule inference} method, which generates new rules in order to `cover' those situations that have been not contemplated in the current set of rules. Thus, a new rule would be created for dealing with the patterns to which the classifier could not assign a class.
The generation of new rules is done by considering the so-called \textit{dictionary}, i.e. a set of terms corresponding to all the possible inputs and actions in the system, which are antecedents and consequents \footnote{The antecedents are the conditions of a rule that have to be met to apply the consequents.} in the security rules to be inferred.
The evaluation of these rules is done by considering the stored log information concerning the parameters along with the actions and decisions made in every component in the system. Thus, it is possible to `simulate' the whole system behaviour when the new rule is included and get a value of its performance.
Finally, the inferred rules are proposed to the CSO as ``new, but not yet refined'', along with their evaluated performance.

@@

\item A \textit{GA optimisation} algorithm for adapting the assets' values. These are numerical representations of the importance of the corporate assets, and are considered in the Real-Time Risk and Trust Analysis process, in order to assign a risk value to every potential decision that can be made by the system.
By evaluating the partial solutions proposed by the GA, this approach provides the CSO, who is in charge of assigning and adjusting these values over time, with information about the most dangerous situations for certain assets.
The adaptation or adjustment concerns the change in the value that an asset has due to a loss of importance, for instance, for being and out-to-date document.

>>>>

\item A \textit{GP rule inference} method, which generates new rules in order to `cover' those situations that have been not contemplated in the current set of rules. Thus, a new rule would be created for dealing with the patterns to which the classifier could not assign a class.
The generation of new rules is done by considering the so-called \textit{dictionary}, i.e. a set of terms corresponding to all the possible context situations and user actions in the system, which are the antecedents and consequents \footnote{The antecedents are the conditions of a rule that have to be met to apply the consequents.} of the security rules to be inferred.
The evaluation of these rules is done by considering the information that has been described. Thus, it is possible to `simulate' the whole system behaviour when the new rule is included. Therefore, the system gets a value of its performance in terms of, for instance, how many of the events that were not classified or misclassified, are covered now. As was also mentioned, the user or device trust values have influence in the creation of the rules.
Finally, the inferred rules are proposed to the CSO as ``new, but not yet refined'', along with their evaluated performance.

@@

\item A \textit{GA optimisation} algorithm for adapting the assets' values. These are numerical representations of the importance of the corporate assets, and are considered in the Real-Time Risk and Trust Analysis process, in order to assign a risk value to every potential decision that can be made by the system.
By evaluating the partial solutions proposed by the GA, this approach provides the CSO, who is in charge of assigning and adjusting these values over time, with information about the most dangerous situations for certain assets. The context information that is gathered by the system is very important, then, in this process.
The adaptation or adjustment concerns the change in the value that an asset has due to a loss of importance, for instance, for being and out-to-date document.
